Roster Review (Generic)

### 2019-06-11 rosterReview_generic.Rmd
Latest rosters, many big trades lately

team_pos_avg_zar %>% 
  ungroup() %>% 
  group_by(team) %>% 
  summarize(ovrl_avg_pos_zar = mean(avg_pos_zar),
            var_pos_zar = sd(avg_pos_zar)) %>% 
  arrange(ovrl_avg_pos_zar %>% desc)

>>>>

#TODO 3 OFs, players with multiple positions, avoid bench players
team_pos_avg_zar %>% 
  ungroup() %>% 
  group_by(team) %>% 
  summarize(sum_pos_zar = sum(avg_pos_zar),
            mean_pos_zar = mean(avg_pos_zar),
            var_pos_zar = sd(avg_pos_zar)) %>% 
  arrange(mean_pos_zar %>% desc)
